%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Mariappan Ramasamy
%
% Repository:
% https://github.com/mariappan/resume
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\documentclass[]{mariappan-resume}
\begin{document}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     COLUMN ONE
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{minipage}[t]{0.33\textwidth} 
\begin{large}
	\headername{Mariappan Ramasamy}\\
\end{large}
\custombold{Senior Member of Technical Staff\\
at VMware Software India Pvt. Ltd.}


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     SKILLS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Skills}
\noindent\rule[3mm]{5cm}{0.4pt}
\subsection{Platforms}
Linux, MacOS
\vspace{6pt}
\subsection{Languages}
C, C++, Python, Shell Scripting,\\
XML, XSL, Yang
\vspace{6pt}
\subsection{RTOS}
MQX, MQXLite, Micrium
\vspace{6pt}
\subsection{Protocols}
TCP/IP, DNS, DHCP, HTTP, VLAN,\\
RSTP, LACP, BGP, VRRP, VLT
\vspace{6pt}
\subsection{Tools}
JTAG, Gdb, Valgrind, Git, Wireshark\\
tcpdump, Iptables, Ebtables
\vspace{6pt}
\subsection{Others}
Agile Methodology, Virtual Machines,\\
AWS, LXC Containers, Docker

\sectionsep
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     ACHIEVEMENTS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Achievements}
\noindent\rule[3mm]{5cm}{0.4pt}

\subsection{Best Performer}
Received Best performer award for\\
2013 at Qualcomm.
\vspace{6pt}

\subsection{Champion Award}
Received champion award twice and\\
silver award at Dell EMC.
\vspace{6pt}

\subsection{Dell Hackathon}
Developed an application to monitor\\
network switches for any anomalies\\
and take corrective actions.

\sectionsep
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     EDUCATION
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Education} 
\noindent\rule[3mm]{5cm}{0.4pt}\\
\datecolor{2006-2010}
\subsection{Bachelor of Engineering} 
Electronics and Communication Engineering \\
Coimbatore Institute of Technology \\
Coimbatore, India \\
CGPA : 8.28/10\\
\vspace{8pt}

\datecolor{2018-Present}
\subsection{Master of Technology} 
Software Engineering \\
BITS, Pilani. 

\vspace{8pt}

\sectionsep
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     COLUMN TWO
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\end{minipage} 
\hfill
\begin{minipage}[t]{0.66\textwidth} 
% \descript{BS in Computer ence}
\hspace*{0pt}\hfill    \\
\hspace*{0pt}\hfill    \\
\hspace*{0pt}\hfill G4B, Govindan Nagar, Palavakkam \\
\hspace*{0pt}\hfill Chennai, TamilNadu - 600 041, India \\
\hspace*{0pt}\hfill Mob: +91 94861 42301 \\
\hspace*{0pt}\hfill Email:\textbf{\href{mailto:rmariappan@outlook.com}{ rmariappan@outlook.com}} \\
\hspace*{0pt}\hfill Linkedin:\textbf{\href{https://www.linkedin.com/in/mariappanr}{www.linkedin.com/in/mariappanr}}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     EXPERIENCE
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Experience(8+ Years)}
\noindent\rule[3mm]{12.5cm}{0.4pt}
\datecolor{2018-Now} \runsubsection{VMware}
\descript{Senior Member of Technical Staff}
\noindent
\hspace{5em}%
\begin{minipage}{0.85\textwidth\vspace{2pt}}
Involved in the development of cloud based SD-WAN solution.\\
Added support for stateful NAT to aid in flow persistence on the controller (high-availability).\\
Hands on experience with POSIX based multi-threaded programming and synchronization.\\
Contributed to various modules namely inbound/outbound firewall, overlay protocol enhancements, policy nat, etc.
\end{minipage}
\descriptright{C, Python, Linux, iptables, SDN, Virtualisation}
\sectionsep

\datecolor{2015-2018} \runsubsection{Dell EMC}
\descript{Network Dev Senior Engineer}
\noindent
\hspace{5em}%
\begin{minipage}{0.85\textwidth\vspace{2pt}}
Designed and developed Virtual Link Trunking (VLT) protocol for the new Linux based Dell Network Operating System OS10.\\
Developed a module to use Redis based infrastructure to sync messages between peers for MAC and ARP sync.\\
Developed yang models for communication between various protocols like LACP, xSTP. \\
Unit test and Automation of VLT test cases.\\
Enhanced VRRP protocol to support active-active mode for VLT usecase using ebtables.\\
Involved in the development of management infra and CLI for the OS10 Network Operating system.\\
Enhanced the open-source klish framework to support yang based transactions and handle recursive arguments.

\end{minipage}
\descriptright{C, Python, C++, XML, XSL, Yang, Redis, ebtables, Linux}
\sectionsep

\datecolor{2012-2014} \runsubsection{Qualcomm}
\descript{Engineer}
\noindent
\hspace{5em}%
\begin{minipage}{0.85\textwidth\vspace{2pt}}
Early member of the startup firmware team that helped integrating entire TCP/IP stack into the 802.11n WLAN Chip and developed IOT solution.\\
Integrated open source webio HTTP server stack into the WLAN firmware and implemented a primitive file-system to store files in flash in Asynchronous mode.\\
Sole developer in implementing the mini HTTP client protocol in the firmware.\\
Enhanced host driver for microprocessors to work with multiple interface support.
\end{minipage}
\descriptright{C, JTAG, FPGA, Shell scripting, IOT}
\sectionsep

\datecolor{2010-2012} \runsubsection{Aricent}
\descript{Software Engineer}
\noindent
\hspace{5em}%
\begin{minipage}{0.85\textwidth\vspace{2pt}}
Worked in Intelligent Services Access Manager (ISAM/ IP-DSLAM) project to handle hot reset and the issues associated with it like filter-mapping.\\
Working knowledge in VLAN, RSTP, and LACP through bug fixes in aricent stack ISS (Intelligent Switch Software).

\end{minipage}
\descriptright{C, C++, Perl, Broadcomm NPU}

\end{minipage} 
\end{document}